{\normalsize Seminar: Formal Specification} \\[1ex] Security of Multithreaded Programs by Compilation\cite{Barthe07}

### 2012-01-18 paper/paper.tex
added figure around the extention of the sequential typing rules
forgot to add label
added one more sentence
give figure label a better name
added two examplary typing rules for the assembly language

\todo{Place proofstrees into one line with minipages}
\begin{prooftree}
\AxiomC{P[i] $\in$ SeqIns}
\AxiomC{$se, i \vdash_{seq} s \Rightarrow t$}
\BinaryInfC{$se, i \vdash s \Rightarrow t$}
\end{prooftree}

\begin{prooftree}
\AxiomC{P[i] = \texttt{start} pc}
\AxiomC{$se(i) \leq se(pc)$}
\BinaryInfC{$se, i \vdash s \Rightarrow s$}
\end{prooftree}

@@

Besides this concrete language we need to define a type system to enforce noninterference
according to \ref{sec:typesystem}. The local types are defined by a stack of security levels
$LType = Stack(Level)$ and $t_{init}$ with the empty stack.

>>>>

\todo{Place proofstrees into one line with minipages}
\begin{figure}
\begin{prooftree}
\AxiomC{P[i] $\in$ SeqIns}
\AxiomC{$se, i \vdash_{seq} s \Rightarrow t$}
\BinaryInfC{$se, i \vdash s \Rightarrow t$}
\end{prooftree}

\begin{prooftree}
\AxiomC{P[i] = \texttt{start} pc}
\AxiomC{$se(i) \leq se(pc)$}
\BinaryInfC{$se, i \vdash s \Rightarrow s$}
\end{prooftree}
\caption{Extension of the sequential typing rules}
\label{fig:multithreaded-typing-rules}
\end{figure}

@@

Besides this concrete language we need to define a type system to enforce noninterference
according to \ref{sec:typesystem}. The local types are defined by a stack of security levels
$LType = Stack(Level)$ and $t_{init}$ with the empty stack. The typing rules defined in
Figure~\ref{fig:multithreaded-typing-rules} need to be extended with rules for the concrete instructions
of the assembly language. In this summary I only explain two of them, the rest follows
in a similar manner.

\todo{beautify me}
\begin{figure}
\begin{prooftree}
\AxiomC{$P[i] = store\ x$}
\AxiomC{$se(i) \sqcup k \leq \Gamma(x)$}
\BinaryInfC{$se, i \vdash_{seq} k :: st \Rightarrow st$}
\end{prooftree}

\begin{prooftree}
\AxiomC{$P[i] = ifeq\ j$}
\AxiomC{$\forall j' \in reg(i), k \leq se(j')$}
\BinaryInfC{$se, i \vdash_{seq} k :: st \Rightarrow lift_k(st)$}
\end{prooftree}
\caption{Excerpt of typing rules for the assembly language}
\label{fig:transfer-rules}
\end{figure}
